Supplementary Information

### 2021-02-17 doc/manuscript/ForestGEO_treerings.Rmd
update affiliations

[Kristina J. Anderson-Teixeira^1,2^*](0000-0001-8461-9713),
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Ross Alexander^5^,
Craig D. Allen^6^,
Raquel Alfaro-Sánchez^7^,
Tala Awada^8^,
Jennifer L. Baltzer^7^,
Patrick J. Baker^9^,
Sarayudh Bunyavejchewin^10^,
Paolo Cherubini^11^,
Justin Cooper^12^,
Stuart J. Davies^2^,
Cameron Dow^1,13^,
Ryan Helcoski^1^,
[Jakub Kašpar](0000-0003-1780-6310)^14^,
[James Lutz]( 0000-0002-2560-0710)^15^,
Ellis Q. Margolis^6^,
Justin Maxwell^16^,
Sean McMahon^2,17^,
Camille Piponiot^1,2,18^,
Sabrina Russo^8^,
[Pavel Šamonil](0000-0002-7722-8797)^14^,
Anastasia Sniderhan^7^,
Alan J. Tepley^1,19^,
[Ivana Vašíčková](0000-0002-6070-5956)^14^, 
Mart Vlam^20^,
Peter Zuidema^20^

@@

6. U.S. Geological Survey, Fort Collins Science Center, Jemez Mountains Field Station, Los Alamos, NM 87544, USA

@@

16. Department of Geography, Indiana University, Bloomington, Indiana, USA

17. Smithsonian Environmental Research Center, Edgewater, MD, USA

18. CIRAD, Montpellier, France

19. Canadian Forest Service, Northern Forestry Centre, Edmonton, Alberta, Canada

20. Forest Ecology and Forest Management Group, Wageningen; Wageningen, The Netherlands

>>>>

[Kristina J. Anderson-Teixeira^1,2^*](0000-0001-8461-9713),
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Ross Alexander^5^,
Craig D. Allen^6^,
Raquel Alfaro-Sánchez^7^,
Tala Awada^8^,
Jennifer L. Baltzer^7^,
Patrick J. Baker^9^,
Sarayudh Bunyavejchewin^10^,
Paolo Cherubini^11^,
Justin Cooper^12^,
Stuart J. Davies^2^,
Cameron Dow^1,13^,
Ryan Helcoski^1^,
[Jakub Kašpar](0000-0003-1780-6310)^14^,
[James Lutz]( 0000-0002-2560-0710)^15^,
Ellis Q. Margolis^16^,
Justin Maxwell^17^,
Sean McMahon^2,18^,
Camille Piponiot^1,2,19^,
Sabrina Russo^8^,
[Pavel Šamonil](0000-0002-7722-8797)^14^,
Anastasia Sniderhan^7^,
Alan J. Tepley^1,20^,
[Ivana Vašíčková](0000-0002-6070-5956)^14^, 
Mart Vlam^21^,
Peter Zuidema^21^

@@

6. Department of Geography & Environmental Studies, University of New Mexico; Albuquerque, NM  87131  USA

@@

16. U.S. Geological Survey, Fort Collins Science Center, Jemez Mountains Field Station, Los Alamos, NM 87544, USA

17. Department of Geography, Indiana University, Bloomington, Indiana, USA

18. Smithsonian Environmental Research Center, Edgewater, MD, USA

19. CIRAD, Montpellier, France

20. Canadian Forest Service, Northern Forestry Centre, Edmonton, Alberta, Canada

21. Forest Ecology and Forest Management Group, Wageningen; Wageningen, The Netherlands
